Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-08-13 man/figures/bai_cronos.Rmd
modify figures and add eps

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
source(here::here('/script/R/colores_den.R'))

@@

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("stringr")
library("pander")
library("lemon")
library("magrittr")
source(here::here('/script/R/custom_functions.R'))

@@

```{r}
# SAVE as eps

saveImage(plot_bai_s, path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_4", u = "cm") 
```

### 2019-08-13 man/figures/browning.Rmd
modify figures and add eps

```{r pkg}
library("tidyverse")
library("here")
library("scales")
library("viridis") # colours 
library("ggthemes") # colours 
```

@@

>>>>

```{r pkg}
library("tidyverse")
library("here")
library("scales")
library("viridis") # colours 
library("ggthemes") # colours 
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
saveImage(per_pixels_green, path="./man/figures/svg/", dpi=300, w=14, h=14, fig= "fig_3", u = "cm") 
```

### 2019-08-13 man/figures/corr_plot_years.Rmd
modify figures and add eps

library("grid")
# library("GGally")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

@@

>>>>

library("grid")
# library("GGally")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
# SAVE as eps 
saveImage(g , path="./man/figures/svg/", dpi=300, w=20, h=10, fig= "fig_s5", u = "cm") 
```

### 2019-08-13 man/figures/correla_boot_sites.Rmd
update text and figures
modify figures and add eps

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

**Figure S6.** Correlation among site chronologies (CA-High, CA-Low and SJ) in different time-domains after pre-filtering the time-series with increasing size of the moving-average window (1 to 40 years). Each site chronology was smoothed using centred moving averages with different window sizes (1 to 40 years), and then Pearson's correlation coefficient between the each pair chronologies were calculated. Significance was tested using 1000 boostrap replicates and with 95 % confidence intervals built using the R packgae `boot` [@Canty2016].

@@

>>>>

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
source(here::here('/script/R/custom_functions.R'))
```

**Figure S6.** Correlation among site chronologies (CA-High, CA-Low and SJ) in different time-domains after pre-filtering the time-series with increasing size of the moving-average window (1 to 40 years). Each site chronology was smoothed using centred moving averages with different window sizes (1 to 40 years), and then Pearson's correlation coefficient between the each pair chronologies were calculated. Significance was tested using 1000 boostrap replicates and with 95 % confidence intervals built using the R packgae `boot`.

@@

```{r}
# SAVE as eps 
saveImage(correla_sitesSJCALH , path="./man/figures/svg/", dpi=300, w=20, h=14, fig= "fig_s6", u = "cm") 
```

### 2019-08-13 man/figures/cumulative_prec.Rmd
modify figures and add eps

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
```

@@

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("ggrepel")
library("scales")
library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
# SAVE as eps 
saveImage(p, path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_s1", u = "cm") 
```

### 2019-08-13 man/figures/evi_vs_severe_droughts.Rmd
modify figures and add eps

```{r load_pkg}
library("tidyverse")
library("here")
library("lubridate")
library("anytime")
library("rdryad")
library("scales")
```

@@

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("lubridate")
library("anytime")
library("rdryad")
library("scales")
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
# SAVE as eps 
saveImage(combinado2, path="./man/figures/svg/", dpi=300, w=20, h=14, fig= "fig_s7", u = "cm") 
```

### 2019-08-13 man/figures/gc_perc_trees.Rmd
modify figures and add eps

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
```

@@

>>>>

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
# SAVE as eps 
saveImage(pgc_median50 , path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_s4", u = "cm") 
```

### 2019-08-13 man/figures/growth_changes.Rmd
modify figures and add eps

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
```

@@

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = 'gray', width = .35, size = .2, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.2) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black', lwd=0.2) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.text.y = element_text(size = 5.5),
          axis.text.x = element_text(size = 6)) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

@@

```{r}
# azul, verde, rojo 
# CaH, CaL, SJ 
colores_den <- c("#56B4E9","#009E73","#CD5C5C")
```

@@

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
source(here::here('/script/R/custom_functions.R'))
```

@@

  p <- ggplot(df, aes_string(x = x, y = y)) +
    geom_errorbar(mapping = yerrorbar, colour = micolor, width = .35, size = .2, 
                  na.rm = TRUE) + 
    geom_bar(stat = 'identity', fill = micolor, colour = micolor) +
    geom_hline(yintercept = 0, colour = 'black', lwd = 0.2) + 
    ylab(my_ylab) +
    # Add line to %GC = 50 
    geom_hline(yintercept = c(50, -50), linetype=2, colour='black', lwd=0.2) +
    theme_bw() +
    theme(panel.grid = element_blank(),
          axis.text.y = element_text(size = 5.5),
          axis.text.x = element_text(size = 6)) +
    coord_cartesian(xlim=limitesX)
    # Customize limits and breaks to min of year data 
  p
}

@@

@@

```{r}
saveImage(gg, path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_5", u = "cm") 
```

### 2019-08-13 man/figures/plot_spei12.Rmd
update text and figures
modify figures and add eps

```{r load_pkg}
library("tidyverse")
library("here")
```

@@

**Figure S2**. Drought severity in the Sierra Nevada for the 1901-2016 period based on the Standardised Precipitation-Evapotranspiration Index (SPEI). Data from Global SPEI database (http://spei.csic.es/database.html). We obtanied the SPEI data for a 12 month scale and for all 0.5º grid cells covering Sierra Nevada. Horizontal gray bars indicate 2005 and 2012 year.

@@

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
source(here::here('/script/R/custom_functions.R'))
```

@@

**Figure S2**. Drought severity in Sierra Nevada for the 1901-2016 period based on the Standardised Precipitation-Evapotranspiration Index (SPEI). Data from Global SPEI database (http://spei.csic.es/database.html). We obtanied the SPEI data for a 12 month scale and for all 0.5º grid cells covering Sierra Nevada. Horizontal gray bars indicate 2005 and 2012 year.

@@

```{r}
# SAVE as eps 
saveImage(s, path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_s2", u = "cm") 
```

### 2019-08-13 man/figures/residual_chronos.Rmd
modify figures and add eps

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
source(here::here('/script/R/colores_den.R'))
```

@@

>>>>

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
# SAVE as eps 
saveImage(plot_rwi_crono , path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_s3", u = "cm") 
```

### 2019-08-13 man/figures/resilience_long_term.Rmd
modify figures and add eps

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
library("broom")
library("cowplot")
library("purrr")
library("ggpubr")
library("rstatix")
library("ggpmisc")
source(here::here('/script/R/colores_den.R'))
```

@@

```{r}
# SAVE as eps 
ggsave(filename = here::here("./man/figures/svg/fig_6.jpg"), 
       dpi = 300,  plot=res_long_term_sites_all, width=25, height=14, units = "cm")
ggsave(filename = here::here("./man/figures/svg/fig_6.eps"), 
       dpi = 300,  plot=res_long_term_sites_all, width=25, height=14, units = "cm")
ggsave(filename = here::here("./man/figures/svg/fig_6.svg"), 
       dpi = 300,  plot=res_long_term_sites_all, width=25, height=14, units = "cm")

@@

```{r}
# SAVE as eps 
ggsave(filename = here::here("./man/figures/svg/fig_s8.jpg"), 
       dpi = 300,  plot=res_long_term_sites_no95, width=25, height=14, units = "cm")
ggsave(filename = here::here("./man/figures/svg/fig_s8.eps"), 
       dpi = 300,  plot=res_long_term_sites_no95, width=25, height=14, units = "cm")
ggsave(filename = here::here("./man/figures/svg/fig_s8.svg"), 
       dpi = 300,  plot=res_long_term_sites_no95, width=25, height=14, units = "cm")

>>>>

```{r load_pkg}
library("tidyverse")
library("here")
library("scales")
library("patchwork")
library("ggrepel")
library("broom")
library("cowplot")
library("purrr")
library("ggpubr")
library("rstatix")
library("ggpmisc")
source(here::here('/script/R/custom_functions.R'))
```

@@

```{r}
# SAVE as eps 
saveImage(res_long_term_sites_all, path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_6", u = "cm") 
```

@@

```{r}
# SAVE as eps 
saveImage(res_long_term_sites_no95, path="./man/figures/svg/", dpi=300, w=25, h=14, fig= "fig_s8", u = "cm")
